\documentclass{tufte-handout}

\title{From Idea to Publication: managing projects for academic work}

\author[lmp]{Luke M Perez, University of Texas at Austin}

%\date{28 March 2010} % without \date command, current date is supplied

% \geometry{showframe} % display margins for debugging page layout

\usepackage{graphicx} % allow embedded images
  \setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
  \graphicspath{{graphics/}} % set of paths to search for images
\usepackage{amsmath}  % extended mathematics
\usepackage{booktabs} % book-quality tables
\usepackage{units}    % non-stacked fractions and better unit spacing
\usepackage{multicol} % multiple column layout facilities
\usepackage{lipsum}   % filler text
\usepackage{fancyvrb} % extended verbatim environments
  \fvset{fontsize=\normalsize}% default font size for fancy-verbatim environments

% Standardize command font styles and environments
\newcommand{\doccmd}[1]{\texttt{\textbackslash#1}}% command name -- adds backslash automatically
\newcommand{\docopt}[1]{\ensuremath{\langle}\textrm{\textit{#1}}\ensuremath{\rangle}}% optional command argument
\newcommand{\docarg}[1]{\textrm{\textit{#1}}}% (required) command argument
\newcommand{\docenv}[1]{\textsf{#1}}% environment name
\newcommand{\docpkg}[1]{\texttt{#1}}% package name
\newcommand{\doccls}[1]{\texttt{#1}}% document class name
\newcommand{\docclsopt}[1]{\texttt{#1}}% document class option name
\newenvironment{docspec}{\begin{quote}\noindent}{\end{quote}}% command specification environment

% Bibliography 
% \usepackage[english]{babel}
% \usepackage[authordate,bibencoding=auto,strict,backend=bibtex,natbib]{biblatex}
% \addbibresource{Proj_MGT.bib}


\begin{document}



\maketitle% this prints the handout title, author, and date

% \begin{abstract}
% \noindent
% Project management is fundamentally about managing the anxiety
% produced by ``open loops'' and unfinished tasks. This handout surveys
% a few strategies which help close the open loops and increase
% productivity. Your mileage may vary.
% \end{abstract}

%\printclassoptions

\section{Introduction} % (fold)
\label{sec:intro}

\subsection{Close the loops}\marginnote{David Allen \textit{Getting Things Done}} % (fold)
\label{sub:close_the_loops}
Managing projects is, at its core, fundamentally about managing the
anxiety produced by the nagging question in your head ``Oh, don't
forget to do [x].'' As it turns out, human nature is surprisingly
inefficient when it comes to remembering tasks, ``to-do'' lists, and
priorities.
% subsection close_the_loops (end)

\subsection{Apps don't matter} % (fold)
\label{sub:apps_don_t_matter}

You can waste a lot of hours jumping from application to application,
pursuing task-management utopia. But remember that at the end of the
day, what application you use does not matter. Find the ones that work
for you, learn the hell of it.\marginnote{Kieran Healy, \textit{Plain
    Text Guide}} Grasping a few basic concepts for \textit{process}
will serve you much better. Let the tasks determine the tools, not the
other way around.
% subsection apps_don_t_matter (end)
% section introduction (end)

\section{Backward Planning} % (fold)
\label{sec:backward_planning}

The approach that most graduate students think about projects is
progressively linear. From the moment we get an idea or decide to
write a paper, the process usually looks something like the following.

\[ data~ crunch \rightarrow read~ for~ a~ theory \rightarrow recrunch~
  data \rightarrow repeat~ until~ deadline \]
% \[ Idea \righarrow Read \rightarrow Find data? \rightarrow read more \rightarrow cram for the deadline \]

This process is \textit{literally} backwards. Although somewhat of a
caricature of the writing process, some version of this is where most
of us find ourselves most of the time. Parkinson's Law captures the
phenomenon but not the reason why this happens on an individual
level. Open loops cause us to constantly revise, re-read, refine
because we're unsure when the project is 'done'.\marginnote{Pro-Tip:
  it is always a good idea to set your deadline a week before the hard
deadline.} Better is to begin
with the hard deadline and work in reverse-chronological order to
determine all the dependencies which must be accomplished, the time
estimated for each dependency, and the order they must be
finished. The process looks like this:

\[Read \leftarrow Data~ Crunch \leftarrow Write \leftarrow Proof  \leftarrow Revisions \leftarrow Deadline  \]

\noindent For example, if you need a week to proof read something, then
you need to be finished at least one week before you deadline. And if
you write the introduction and conclusions last and those take a few
days, then you need to finish the data-analysis or major portions at
least a week before that. And so forth...\marginnote{Although a bit of
  overkill for graduate students, a Gantt chart captures this concept
  quite well.}
% section backward_planning (end)

\section{In the weeds}
\label{in-weeds}

\subsection{A GTD Crash Course}
\label{gtd-crash-course}

\paragraph{Projects vs Tasks}
\label{sec:proj-tasks}

\begin{enumerate}
\item[] A task is any single action.
\item[] A project is anything that requires two or more actions
\end{enumerate}

\paragraph{A simple example}

Emailing your adviser to ask a question about the grading rubric for a
TA class is a task because it is one action. Attending office hours
for your adviser is a project because you have several dependencies
that are involved: drafting a quick agenda of the two or three items
you need. Emailing him or her the agenda in advance with any
attachments they need so they can be prepared. Spending a few minutes
before you arrive to review your agenda before walking to his or her
office, etc., etc. 


\subsection{Tasks vs Contexts}
\label{tasks-contexts}

Every task you create for yourself belongs to both a project and a
context.\sidenote{Sometimes, the project may just be a catch all for
  all single action tasks.} A \textit{Context} is often described as
the one physical thing or place that is mandatory before the task can
be done. For instance, you need your laptop if you're going to write a
section of your paper but you must be in the building if you're going to drop
off documents to anyone in the front office.\marginnote{Pro-tip: Make
  a context or just a list for every faculty or staff member you
  interact with regularly. When you get two or three items, you have
  an agenda to email them. It let's them know you value their time.} Simple enough. But you
can extend this concept to non-physical things like the day and time
of the week or your energy level. The reason for doing this is that
you can maximize you're overall efficiency through the day.
% subsection Tasks-Contexts (end)

\subsection{Daily and Weekly Review}
\label{sec:review}

Whatever system you use to manage your projects, it will not work if
you do not trust it intuitively. The instant you're not sure if you've
captured all your tasks and projects, you're mind will begin to
``remind'' you---at which point, the anxiety of unfinished work and
open loops will set in. The only way to prevent this is to review
regularly. Spending a few minutes at the start and end of the work day
to review will save you countless hours of time and anxiety. A longer
weekly review helps you keep your eye on the medium- and
long-term.\footnote{David Allen discusses this process in greater
  detail.}


% subsection Review (end)
% section In the Weeds (end)

\section{Writing Projects and GTD}
\label{sec:write-proj-gtd}

\subsection{Basic Principles}
\label{basic-principles}

\begin{enumerate}

  \item Embrace iteration
  \item Write early, write often
  \item Organize efficiently
  \item Outsource your time-management

  \end{enumerate}

\paragraph{Embrace Iteration} No project goes from idea to publication
in one move. Indeed, even your ideas will begin from previous work. So
keep a journal and a pen on you at all times. Tinker, draft, trash,
repeat. Review these ideas regularly and keep a file on your computer
with a list of possible projects and ideas.\marginnote{Lots of people
  prefer to keep a spreadsheet with \textsc{Title, Thesis, Abstract}
  that they can draw from. Over time, you'll have dozens of ideas to
  draw from.}

\paragraph{Write early, Write often} You should be writing 500 words
every day, or at least three or four times per week. The research
shows that scholars who write for short periods more often produce
more work, more frequently than those who write for longer periods in
blocks.\footnote{Paul J. Silva, \textit{How to write a lot.}} One
  reason this works is that it trains yourself to overcome writer's
  block and anxiety about getting started.\marginnote{Steven
    Pressfield calls this ``killing the resistance.''}

\paragraph{Organize efficiently}

I use a database program called \textit{DevonThink} which is best
described as much more advanced version of Evernote. It has an
indexing feature and built-in AI that can find related notes. Writing
notes in plain text with a file name that begins with \texttt{YYYYMMDD
  -- title} will help you find your notes faster whether you use a
program like Evernote, DevonThink, or manual
searching.\marginnote{Think of your notes as digital versions of index
  cards. cf. Umberto Eco, \textit{How to Write a Thesis}}.

\paragraph{Outsource your time-management}

Using a task management system with the concepts outlined above is, I
believe, the key hurdle to getting work out the
door.\footnote{Although unrelated to task management apps, Seth
  Godin's talk on ``the lizard brain'' (google it) makes a similar
  point about product shipment for apps.} I've been using
\textit{OmniFocus}, which is a Mac-only product. The key feature is
that it has companion apps for iOS which lets me stay on top of my
tasks even when I don't have my computer at hand. There are other
apps of course. If you have one, keep using it until it doesn't work
for you. But you could easily do this with a notepad, calendar, and a
pencil.  

\section{Applications} % (fold)
\label{sec:applications}

\paragraph{Currently Using} % (fold)
\label{par:currently_using}
\begin{enumerate}
  \item[] Leuchtturm 1917 Journal and a good pen
  \item[] DevonThink
  \item[] Emacs \& Sublime
  \item[] OmniFocus for Mac and iOS
  \item[] BusyCal
\end{enumerate}
% paragraph currently_using (end)

\paragraph{Previously Used} % (fold)
\label{par:previously_used}

\begin{enumerate}
  \item[] Evernote
  \item[] Scrivener\footnote{Scriverner is strongly encouraged for those who are not comfortable with the command line}
  \item[] Mellel (Word processor)
  \item[] Sente and/or Pages (the citation manager)
\end{enumerate}

% paragraph previously_used (end)

\paragraph{Noteable Mention} % (fold)
\label{par:noteable_mention}

\begin{enumerate}
  \item[] TexPad
  \item[] Mendeley
\end{enumerate}
% paragraph noteable_mention (end)
% section applications (end)
\nocite{*}

% \printbibliography[title=Futher Reading]
\renewcommand{\bibname}{Further Reading} 
\bibliography{Proj_MGT}
\bibliographystyle{plainnat}

\end{document}
